---
title: "HW6"
author: "Amanda Howarth"
date: "11/23/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rvest)
library(tidyverse)
library(purrr)
library(broom)
library(modelr)
library(mgcv)
library(patchwork)
```

## Importing data
```{r}
birthweight = read_csv("./data/birthweight.csv")
```
```{r}
birthweight_clean = birthweight %>% 
  janitor::clean_names() %>% 
  mutate(babysex = factor(babysex, levels = c("1", "2")),
         frace = factor(frace, levels = c("1", "2", "3", "4", "8", "9")),
         mrace = factor(mrace, levels = c("1", "2", "3", "4", "8", "9")),
         malform = factor(malform, levels = c("0", "1")),
         babysex = recode(babysex, "1" = "male", "2" = "female"), 
         frace = recode(frace, "1" = "white", "2" = "black", "3" = "asian", "4" = "puerto rican", "8" = "other", "9" = "unknown"),
         mrace = recode(mrace, "1" = "white", "2" = "black", "3" = "asian", "4" = "puerto rican", "8" = "other", "9" = "unknown"), 
         malform = recode(malform, "0" = "absent", "1" = "present")) %>%
  rename(bwt_grams = bwt, mom_weight_lbs = delwt, family_income = fincome, father_race = frace, mom_race = mrace, ges_age_weeks = gaweeks, age_menarche = menarche, mom_height = mheight, mom_age = momage, mom_pre_bmi = ppbmi)
```

## Model building
I have hypothesized that a baby's physical and biological characteristics as well as the mother's physical and biological characteristics at the time of delivery would affect the baby's weight at birth. Thus, in building my model I analyzed baby's sex, head circumference, baby length, gestational age, and presence of malformations that would affect weight. Additionally, I analyzed mother's weight, age at delivery, and height. 

* say that u removed some bc it did not increase in the R^2 
* say looked at all of them first and then chose significant ones 
* say teh R^2 value 
* reisduals ? predictions? 
* removed malform bc not significant 

```{r}
fit_bwt_model = lm(bwt_grams ~ babysex + bhead + blength + mom_weight_lbs + ges_age_weeks, data = birthweight_clean)

fit_bwt_model %>% 
  broom::tidy() %>% 
  knitr::kable()

fit_bwt_model %>%
  broom::glance() %>% 
  knitr::kable()
```

Show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.
```{r}
birthweight_clean %>% 
  modelr::add_residuals(fit_bwt_model) %>% 
  modelr::add_predictions(fit_bwt_model) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point() + labs(
    y = "Residuals", 
    x = "Predicted values of Birthweight", 
    title = "Residuals Plotted Against Birthweight"
    
  )
```

## Model using using length at birth and gestational age as predictors (main effects only)

```{r}
sample_model_1 = lm(bwt_grams ~  blength + ges_age_weeks, data = birthweight_clean)

sample_model_1 %>% 
  broom::tidy() %>% 
  knitr::kable()

sample_model_1 %>% 
  broom::glance() %>% 
  knitr::kable()
```

## Model using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
sample_model_2 = lm(bwt_grams ~ bhead + blength + babysex + bhead*blength + bhead*babysex + babysex*blength + bhead*blength*babysex, data = birthweight_clean)

sample_model_2 %>% 
  broom::tidy() %>% 
  knitr::kable()

sample_model_2 %>% 
  broom::glance() %>% 
  knitr::kable()
```

## Cross Validation 

```{r}
cv_df = 
  crossv_mc(birthweight_clean, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)
         ) %>% 
  mutate(fit_bwt_model = map(train, ~lm(bwt_grams ~ babysex + bhead + blength + mom_weight_lbs + ges_age_weeks, data = .x)), 
         sample_model_1= map(train, ~lm(bwt_grams ~ blength + ges_age_weeks, data = .x)),
         sample_model_2= map(train, ~lm(bwt_grams ~ bhead + blength + babysex + bhead*blength + bhead*babysex + babysex*blength + bhead*blength*babysex, data = .x))) %>%
  mutate(rmse_1 = map2_dbl(fit_bwt_model, test, ~rmse(model = .x, data = .y)),
         rmse_2 = map2_dbl(sample_model_1, test, ~rmse(model = .x, data = .y)),
         rmse_3 = map2_dbl(sample_model_2, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse, fill = model)) + geom_violin() + labs(
    y = "Root Mean Squared Errors", 
    x = "Models", 
    title = "Root Mean Squared Errors (RMSE's) Across Models"
  )

```

## Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
## Drawing repeated samples with replacement.
```{r}
boot_sample = function(df) {
  sample_frac(weather_df, replace = TRUE)
}

boot_straps = 
  data_frame(
    strap_number = 1:5000,
    strap_sample = rerun(5000, boot_sample(weather_df))
  )
boot_straps
```

## Analyzing bootstrap samples: Log(B0 * B1)
```{r}
bootstrap_results1 = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(cols = c(results)) %>% 
  select(strap_number, term, estimate) %>%
  pivot_wider(
    names_from = "term", 
    values_from = "estimate") %>%
  janitor::clean_names() %>% 
  mutate(log_estimate = log(intercept*tmin)) %>% 
  select(log_estimate)

```

## Analyzing bootstrap samples: R^2
```{r}
bootstrap_results2 = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)) %>% 
      select(-strap_sample, -models) %>% 
  unnest(cols = c(results)) %>% 
  select(r.squared)
```

## Plot the distribution of your estimates, and describe these in words. 
```{r}
plot_log_estimate = bootstrap_results1 %>% 
   ggplot(aes(x = log_estimate)) + geom_histogram() + labs(
    y = "Count", 
    x = "Log(B_0 * B_1)", 
    title = "Distribtuion of Log(B_0 * B_1)"
  )
plot_log_estimate

plot_r_squared = bootstrap_results2 %>% 
  ggplot(aes(x = r.squared)) + geom_histogram() + labs(
    y = "Count", 
    x = "R Squared", 
    title = "Distribtuion of R Squared ")
plot_r_squared 

plot_log_estimate + plot_r_squared 
```
Both distributions above appear to be relatively symmetric. Thus, the left and right hand sides seem to nearly mirror each other within the histograms. There is very slight left skew present in the histogram of R-squared. Because the distribution is approximately symmetric for the histogram of the log of B0 * B1, the mean, median, and mode would all be approximately equal to 2.01 for log of B0*B1. 
For the histogram of R-squared, I will assume the histogram approximately follows a symmteric distribution, and thus its mean, median and mode would be the same value of ~0.91. 

Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂ 2 and log(β̂ 0∗β̂ 1)
```{r}
quantile(pull(bootstrap_results1, log_estimate), c(.0275, .975)) 
# 2.75% = 1.9638   97.5% = 2.0592

quantile(pull(bootstrap_results2, r.squared), c(.0275, .975)) 
# 2.75% = 0.8946   97.5% = 0.9273
```
From the results above, we find that the confiden

